Cover Times of Random Walks

### 2019-04-13 paper.tex
rearrange electrical networks section and citations

@@

\section{Electrical Networks}
\cite{DS84}
There are many connections between electrical networks
and random walks.
Physical properties like voltage, current, and resistance
all have probabilistic interpretations.
In this section, we explore electrical networks to build intuition about 
random walks and motivate a result we use to bound cover times.

We now have the requisite background to prove a result
we will use to bound cover times.
Define the probability $\pr_a(T_b < T_a)$ that starting at $a$
we reach $b$ before returning to $a$.
(Recall that $T_a>0$.)
Now define the effective conductance $\Ceff$ as $i_a/v_a$.

Now our job is to interpret $\Reff C$.
Recall that $\pr_a(T_b < T_a)$ is the probability, starting from $a$,
that we get to $b$ before returning to $a$.
We do independent trials, starting from $a$, until we reach $b$ before $a$.
Each ``failure'' resets the process so $\pr_a(T_b < T_a)$ is geometrically distributed.
Then the expected value $1/\pr_a(T_b < T_a)$ is the expected number of times
we return to $a$ before we finally reach $b$ (and again return to $a$).

Recall that $\pi_a$ is the probability that $(X_t) = a$.
By the same argument, $1/\pi_a$ is the expected return time to $a$.

Thus the expected time from $a$ to $b$ and back is
the product of the expected number of times we return to $a$ before reaching $b$
and the expected return time to $a$.
The commute time identity follows
\begin{align}
E_a[T_b] + E_b[T_a] = \frac{1}{\pi_a}\frac{1}{\pr_a(T_b < T_a)} = \Reff C.
\label{eqn:commute}
\end{align}

@@

The Matthews Method is an example of a remarkably good bound.
In fact, it is tight for the complete graph:
the expected time between any two vertices
is $n-1$ so $\hit = n-1$ and \cref{thm:matthews} gives
us the main result of \cref{sec:complete}.

In addition, the proof uses strategies we employed on the
simple cycle and follows an intuitive structure.

@@

\subsubsection{Balanced Trees}
\cite{LP17} 11.3

>>>>

\subsection{Electrical Networks \label{sec:electric}}

There are many connections between electrical networks
and random walks \cite{DS84}.
Physical properties like voltage, current, and resistance
all have probabilistic interpretations.
In this section, we explore electrical networks to build intuition about 
random walks.

@@

@@

The Matthews Method is an example of a remarkably good bound \cite{LP17}.
In fact, it is tight for the complete graph:
the expected time between any two vertices
is $n-1 = \hit$ and \cref{thm:matthews} gives
us the main result of \cref{sec:complete}.

An added benefit is that the proof uses strategies we employed on the
simple cycle and follows an intuitive structure.

@@

\subsection{Commute Time Identity}
Recall \cref{sec:electric}.
Define the probability $\pr_a(T_b < T_a)$ that starting at $a$
we reach $b$ before returning to $a$.
(Recall that $T_a>0$.)
Now define the effective conductance $\Ceff$ as $i_a/v_a$
and the effective resistance $\Reff$ as $1/\Ceff$.

Recall that $\pr_a(T_b < T_a)$ is the probability, starting from $a$,
that we get to $b$ before returning to $a$.
We do independent trials, starting from $a$, until we reach $b$ before $a$.
Each ``failure'' resets the process so $\pr_a(T_b < T_a)$ is geometrically distributed.
Then the expected value $1/\pr_a(T_b < T_a)$ is the expected number of times
we return to $a$ before we finally reach $b$ (and again return to $a$).

Recall that $\pi_a$ is the probability that $(X_t) = a$.
By a similar argument, $1/\pi_a$ is the expected return time to $a$.

Thus the expected time from $a$ to $b$ and back is
the expected number of returns to $a$ before we reach $b$ times
the expected number of steps for each return to $a$.
The commute time identity follows
\begin{align}
E_a[T_b] + E_b[T_a] = \frac{1}{\pi_a}\frac{1}{\pr_a(T_b < T_a)} = \Reff C.
\label{eqn:commute}
\end{align}

\subsection{Matthews Method on Balanced Trees}
\cite{LP17} 11.3
